### 2020-07-05 README.Rmd
[docs] Update README

This repository contains the data and code for our paper:

> `r Author`, (2020). _`r Title`_. `r Journal` <https://doi.org/xxx/xxx>

Our pre-print is online here:

> `r Author`, (2020). _`r Title`_. `r Journal`, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

> `r Author`, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

The latest compiled draft PDF can be downloaded from the `Artifacts`.

```{r, echo = FALSE, out.width = "30%"}
knitr::include_graphics("figures/artifact.png")
```

>>>>

This repository contains the data and code for paper:

> `r Author`, (2020). _`r Title`_. (In review)

@@

> `r Author`, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`.

@@

The latest compiled draft PDF can be downloaded from the `Actions` &#8594; `Artifacts`.
